### 2018-05-22 msc_diploma_cubesat_galgoczi.tex
aa

>>>>

\begin{figure}[h!]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.55\textwidth,origin=c,angle=0]{images/electrons0degspectra.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=90]{images/0mac.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The spectrum measured when the electrons were shot perpendicular to the scintillator (called angle of 0 $^{\circ}$)}
 \end{figure}

\begin{figure}[h!]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/8mac.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
 \end{figure}

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/electronabsorption.png}[H!]
\caption{The ammount of electrons detected from 100.000 shoot in the simulation}
\end{figure}
